\documentclass[11pt]{article}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{enumitem}
\hyphenation{CPSTA}

\begin{document}
\begin{center}
\textbf{Constitution of CPSTA\\ (Competitive Programming St Andrews)}
\end{center}

\begin{enumerate}[label = \Roman*.]

\item \textbf{Title}: 

The society shall be known as “Competitive Programming St Andrews” (abbreviated to \textbf{CPSTA}).

\item \textbf{Aims}: 

The aims of the society shall be as follows:
    \begin{enumerate}[label = \arabic*.]
    \item To organise events related to competitive programming and improving the related algorithmic and problem-solving skills;
    \item To organise the publicising and attendance of these events;
    \item To organise competitive teams to represent St Andrews in external competitions.
    \end{enumerate}

\item \textbf{Affiliation}:

The Society shall be affiliated to the following organisation:

\begin{itemize}
    \item St Andrews University Students' Association
\end{itemize}

\item \textbf{Membership}: 

Any matriculated student of the University of St Andrews shall be eligible to purchase Ordinary Membership to the society.

Anyone, including people not affiliated with the University, may attend any events hosted by CPSTA, unless stated otherwise.

\item \textbf{Executive Committee}: 

There shall be the following Officers, who shall constitute the Executive Committee of the Society:

\begin{itemize}
\item President
\item Treasurer
\item Sponsorship Coordinator 
\item Publicity Officer
\item Competition Organiser
\end{itemize}

All Officers shall be elected at a General Meeting or co-opted by the Committee if no candidate is elected at a General Meeting or in the case of casual vacancy.

The President shall call Committee meetings on his own volition or upon presentation to him of a written request by two-fifths of the voting members of the Committee.  At least 24 hours' notice of a Committee meeting shall be provided to all voting members of the Committee.  The quorum for a Committee meeting shall be at least 2 voting Officers, provided that one of them is the President. 

No Officer shall derive any financial profit or gain by reason of his officership, including favourable rates on goods or services, unless the same benefit is available to any and all members of the Society.

Any member of the Executive Committee, except the President, may resign at any time by giving written notice or notice by electronic transmission thereof to the President. The President may resign at any time by giving written notice or notice by electronic transmission thereof to the Treasurer. Such resignation shall take effect at the time specified therefor or if the time is not specified, upon delivery thereof; and, unless otherwise specified with respect  thereto, the  acceptance of such resignation shall not be necessary to make it effective.

\item \textbf{Duties of Office}:

The \textbf{President} shall:
\begin{itemize}
\item Serve as the primary point of contact between the Students' Association and the Society;
\item Be the general representation of the society;
\item Call, chair and set the agenda for all committee and general meetings, or nominate a suitable delegate to fulfil their responsibilities should they be unavailable;
\item Oversee the smooth operation of the Society;
\item Be a signatory on the bank mandate;
\item Attend the Health and Safety Training during affiliation*;
\item Pass the associated Health and Safety Competency test*;
\item Review and submit all risk assessments on behalf of the Society to the Student's Association*;
\item Keep a record of the Society's risk assessments submitted during their term and pass them on to their successor*;
\item *These duties shall be the sole responsibility of the President and may not be delegated to another officer except in the event of a vacancy in the position;
\item Organise the competitive team to represent St Andrews.
\end{itemize}

The \textbf{Treasurer} shall:
\begin{itemize}
\item Maintain records of the Society's financial activity in accordance with Association Guidelines;
\item Maintain a full and accurate membership roll;
\item Execute any resolution by the Committee to apply to the Students' Association for funding;
\item Be a signatory on the bank mandate.
\end{itemize}

The \textbf{Sponsorship Coordinator} shall:
\begin{itemize}
\item Organise career-related events for the club;
\item Outreach to potential sponsors and recruiters.
\end{itemize}

The \textbf{Publicity Officer} shall:
\begin{itemize}
\item Publicise the society events to the members and wider University community;
\item Manage the online presence of the society and maintaining the social media accounts.
\end{itemize}

The \textbf{Competition Organiser} shall:
\begin{itemize}
\item Recruit problem writers for organising competitions;
\item Help the Publicity Officer Develop with website development;
\item Direct and organise programming competitions.
\end{itemize}

\item \textbf{General Committee}

A General Committee member must be appointed by at least a 3/5 majority decision at a Committee Meeting by the Executive Committee members present at the meeting. Their duties shall be assigned at the time of appointment based on their skill set and strengths. 

A position on the committee shall be held until the next AGM or resignation of the post. 

Any member of the General Committee may resign at any time by giving written notice or notice by electronic transmission thereof to the president. Such resignation shall take effect at the time specified therefor or if the time is not specified, upon delivery thereof; and, unless otherwise specified with respect thereto, the acceptance of such resignation shall not be necessary to make it effective.

\item \textbf{Finance}:

Any debt incurred by the Society shall be satisfied by an equal subscription from all members.

The annual subscription for Ordinary Membership shall be approved at a General Meeting.

Two signatories of the Students' Association shall appear on the Society's bank mandate.

\item \textbf{Constitution}: 

A copy of this constitution shall be available at every committee meeting and general meeting of the society. Any proposed alteration must be passed by the executive committee and requires a 2/3 majority of members present at a General Meeting. 

\end{enumerate}
\end{document}
